---
title: "Assessment 1"
author: "Mungunchimeg Batbayar s4662982"
date: '2022-03-05'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **RMarkdown editing**
R Markdown is used for creating efficient records of data analysis. R Markdown has 2 steps:

**1.** *Creation*:To create an RMarkdown file (.rmd), you use conventional Markdown syntax
alongside chunks of code written in R 

**2.** *Knit*: the Markdown formatting and the R code are evaluated, and an output file (HTML, PDF, etc) is produced.

Resource: [Click here](https://ourcodingclub.github.io/tutorials/rmarkdown/)

This is link the how to insert the link in the .rmd file [Click here](https://rmarkdown.rstudio.com/lesson-8.html)


## **Load the packages and dataset**

```{r}
#install.packages("tidyverse")
library(tidyverse)
library(knitr)

fastfood <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

head(fastfood, 10)

kable(fastfood[1:10, 1:5])
```


