---
title: "Assessment 1"
author: "Mungunchimeg Batbayar s4662982"
date: '2022-03-12'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**PART 1**

*RMarkdown editing*

R Markdown is used for creating efficient records of data analysis. R Markdown has 2 steps:

**1.** *Creation*:To create an RMarkdown file (.rmd), you use conventional Markdown syntax
alongside chunks of code written in R 

**2.** *Knit*: the Markdown formatting and the R code are evaluated, and an output file (HTML, PDF, etc) is produced.

Resource: [Click here](https://ourcodingclub.github.io/tutorials/rmarkdown/)

This is link the how to insert the link in the .rmd file [Click        here](https://rmarkdown.rstudio.com/lesson-8.html)



*Load the packages and data set*


```{r}
#install.packages("tidyverse")
library(tidyverse)
library(knitr)

fastfood <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

head(fastfood, 10)

kable(fastfood[1:10, 1:5])
```



**PART 2**

```{r}
#install.packages("tidyverse")
library(tidyverse)
library(knitr)
library(tidyr)
library(dplyr)
library(skimr)
```


**Task-8**

```{r}
fastfood %>%
  filter(calories >= 1000) %>%
  arrange(calories)
```


**Task-9**

```{r}
dont_eat_this <- fastfood %>%
  filter(total_fat >=40, total_carb >=80) %>%
  arrange(desc(total_carb))

```


**Task-10**

```{r}
heavy_food <- fastfood %>%
  mutate(heavy_food = case_when(calories>500 ~ "heavy", calories<250 ~ "low", TRUE ~ "average"))
```



**Task-11**

```{r}
library(skimr)
skim(fastfood)
```


**Task-12**

```{r}
fastfood %>%
  count(restaurant) %>%
  arrange(desc(n))
```


**Task-13**

```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(average_calories = mean(calories)) %>%
  ungroup()
```


**Task-14**

*1.The average calories of each restaurant*
```{r}
average_calories <- fastfood %>%
  group_by(restaurant) %>%
  summarise(average_calories = mean(calories)) %>%
  ungroup() %>%
  arrange(desc(average_calories)) %>%
  mutate_if(is.numeric, round, digits = 2)
```


*2.The maximum total fat of each restaurant*

```{r}
max_fat <- fastfood %>%
  group_by(restaurant) %>%
  summarise(total_fat = max(total_fat)) %>%
  ungroup() %>%
  arrange(desc(total_fat))
```


*3.The minimum cholesterol of each restaurant*
```{r}
min_cholesterol <- fastfood %>%
  group_by(restaurant) %>%
  summarise(cholesterol = min(cholesterol)) %>%
  ungroup() %>%
  arrange(cholesterol)
```


  
**Task-15**

Total fat of each restaurant:

```{r}
total_fat_per_restaurant <- fastfood %>%
  group_by(restaurant) %>%
  summarise(total_fat = sum(total_fat)) %>%
  ungroup() %>%
  arrange(total_fat)
```

Figure 1a and Figure 1b show the total fat per restaurant. 
Based on 2 variables which are one discrete and another is continuous, geom_col() function is chosen in Figure 1a,  and geom_point function with geom_line is chosen in Figure 1b. 
In addition, text label and reorder functions are used.

```{r}
total_fat_per_restaurant %>%
  mutate(restaurant = fct_reorder(restaurant, total_fat)) %>%
  ggplot(aes(restaurant, total_fat, group = 1, fill = total_fat)) +
  geom_col() +
  scale_fill_viridis_b() +
  coord_flip() +
  geom_text(aes(label = total_fat), fontface = "bold", size = 4, vjust = 0) +
  labs(x = NULL, y = "Total fat", 
       title = "TOTAL FAT OF EACH RESTAURANT", caption = "Figure 1a")

total_fat_per_restaurant %>%
  mutate(restaurant = fct_reorder(restaurant, total_fat)) %>%
  ggplot(aes(restaurant, total_fat, group = 1, color = total_fat)) +
  geom_line() +
  geom_point() +
      coord_flip() +
  geom_text(aes(label = total_fat), fontface = "bold", size = 4, vjust = 0) +
    labs(x = NULL, y = "Total fat", 
       title = "TOTAL FAT OF EACH RESTAURANT", caption = "Figure 1b") +
        theme_light()
```


**Task-16**

```{r}
new_fastfood <- fastfood %>%
  mutate(cholesterol_sodium = cholesterol + sodium)
  
new_fastfood$salad <- NULL
```


**Task-17**

```{r}
Mcdonalds <- fastfood %>%
    select(restaurant, item, sugar, protein) %>%
  filter(restaurant == "Mcdonalds")
 

Mcdonalds %>%
  ggplot(aes(sugar, protein)) +
  geom_point(colour = "red") +
  geom_line() +
  labs(x = "Sugar ", y = "Protein",
       title = "THE PROPOTION OF SUGAR AND PROTEIN", 
       subtitle = "The graph shows the propotion of Mcdonald's fastfoods", caption = "Figure 2") +
  theme_gray() 
```
 
 

**PART 3**

**Task-18**

```{r}
skim(fastfood)

class(fastfood$item)

fastfood$item <- as_factor(fastfood$item)

fastfood %>%
  mutate(item = fct_lump(item, n = 10)) %>%
  count(item)
```

**Task-19**

```{r}
updated_fastfood <- fastfood %>%
  mutate(calories_type = cut_number(calories, n = 3, labels = c("low", "med", "high"))) %>%
  arrange(desc(calories_type))
```

  
  
**Task-20**

```{r}
ggplot(updated_fastfood, aes(calories_type, calories)) +
  geom_boxplot(color = "dark green") +
  facet_wrap(~restaurant) +
    theme_light() +
    labs(x = 'Calories type', y = NULL,  
          title = 'THE CALORIES TYPE PER RESTAURANT',  caption = 'Figure 3')
```


**Task-21**

```{r}
trans_fat_per <- fastfood %>%
  mutate(trans_fat_percent = trans_fat/total_fat*100) %>%
  mutate_if(is.numeric,
            round, 
            digits = 2)
```


**Task-22**

```{r}
fastfood %>%
  ggplot(aes(restaurant, trans_fat)) +
  geom_col(colour = "purple") +
  facet_wrap(~restaurant) +
  coord_flip() +
  theme_bw() +
  labs(x = NULL, y = 'Trans fat',
       title = "DISTRIBUTION OF TRANS FAT EACH RESTAURANT", caption = "Figure 4")
```


**Task-23**

```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(total_fat = mean(total_fat)) %>%
  ungroup() %>%
  arrange(total_fat)
```


**Task-24**

```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(total_fat = mean(total_fat)) %>%
  ungroup() %>%
  arrange(restaurant, total_fat) %>%
  mutate_if(is.numeric, round, digits = 1) %>%
  ggplot(aes(x = reorder(restaurant, - total_fat), y = total_fat, fill = restaurant)) +
  geom_col() +
  geom_text(aes(label = total_fat), fontface = "bold", size = 4, vjust = 0) +
  coord_flip() +
  theme_bw() +
  labs( x = NULL, y = 'Total fat', fill = 'Name of restaurant', 
        title = 'TOTAL FAT PER RESTAURANT', caption = 'Figure 5')
```



  

